---
title: "Data Products"
author: "Christopher M"
date: "Wednesday, February 24, 2016"
output: slidy_presentation
---

## Product Overview

This presentation will provide a breif overview of the Diamond Explorer Application and prediction tool.

https://christophertestaccount.shinyapps.io/Coursera_two/

## Benefits of the Product

- View histograms of different numerical vectors of data
- Drill Down into the data
- Make better sound decisions of the data
- Verify Assumptions
- View a diamonds with a $200 range
- Compare your own diamonds to prediction

## Overview of the dataset

```{r,results='asis'}
library(ggplot2)
library(xtable)
print(xtable(head(diamonds)),type='html')
```

## Our Prediction Model

```{r,results='asis'}
regression_model <- lm(price~table+depth+carat,diamonds)
print(xtable(summary(regression_model)),type='html')

```
- It is not reported in this output but our model is accounting for 85% of the variance which is excellent.
- One thing we can quickly learn is that you want a smaller table and depth measurement because as these increase our price decreases. 